Visualization of [fulle name] Fractional Integrals

### 2019-05-07 fractional/CMJ style files/article-template.tex
added more meat to example section

If we set the value of $\alpha$ to $\sfrac{4}{5}$ and the value of $t$ to 10 in Eq.~\eqref{eq:ex1} we obtain:
\begin{equation}
\label{eq:ex1_specific}
A_{10}^{\sfrac{4}{5}}=\int_{a_{10}^{\frac{4}{5}}(y)}^{b_{10}^{\frac{4}{5}}(y)} f(\tau)~d\tau 
\end{equation}
Let $R_{10}^{\sfrac{4}{5}}$ denote the region which is bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{10}^{\sfrac{4}{5}}(y)$. The region $R_{10}^{\sfrac{4}{5}}$ is depicted and labelled in the right-most panel of Figure.~\ref{??}. 
Moreover, let $A_{10}^{\sfrac{4}{5}}$ denote the area of $R_{10}^{\sfrac{4}{5}}$. We are now in a position to assign a geometric interpretation to Eq.~\eqref{eq:ex1_specific}.  
We can approximate the area of $A_{10}^{\sfrac{4}{5}}$ by summing together the area of $n$ equal width non-rectangular integration strips that inscribe $R_{10}^{\sfrac{4}{5}}$. 
Furthermore, the sides of these non-rectangular integration strips have to be translations of $b_{10}^{\sfrac{4}{5}}(y)$.
If we take the limit of the aforementioned sum as $n\rightarrow \infty$ we obtain $A_{10}^{\sfrac{4}{5}}$, i.e. the region $R_{10}^{\sfrac{4}{5}}$ is made up 
of an infinite number of infinitesimals; all of them being translations of $b_{10}^{\sfrac{4}{5}}(y)$. The special case in which we approximate $A_{10}^{\sfrac{4}{5}}$ using five equal width non-rectangular integration strips is depicted in the right-most panel of Figure~\ref{??}. 
The sides of the aforementioned five integration strips are depicted in Fig.~\ref{??} using dashed lines. Let $\mathsf{B}_{10}^{\sfrac{4}{5}}$ denote the set containing these dashed curves.

Varying both $\alpha$ and $t$ results in Eq.~\eqref{eq:ex1}. In contrast with Eq.~\eqref{eq:ex1_specific}, Eq.~\eqref{eq:ex1} can be associated with a multitude of regions. 
Let $R_{t}^{\alpha}$ denote the region which is bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{t}^{\alpha}(y)$. Moreover, let $A_{t}^{\alpha}$ denote the area of $R_{t}^{\alpha}$ and let $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}=\{R_t^{\alpha}|t\in\mathsf{T},~\alpha\in\mathsf{A}\}$. 
The regions in the set $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}$ are depicted in Fig.~\textbf{??}. The regions that are depicted in each of the panels of Fig.~\ref{??} were generated by varying $t$, whilst keeping the value of $\alpha$ fixed. 
The title of each panel indicate which $\alpha$-value was used to generate the regions depicted in each panel. The only difference between the regions located in each 
panel is their right edges. The right edges of the regions in each panel are depicted using varying shades of gray. The lighter the shade with which an edge is depicted, 
the larger the $t$-value is, that was used to generate it.

As was the case for $R_{10}^{\sfrac{4}{5}}$, each of the regions depicted in Fig.~\ref{} are made up of an infinite number of infinitesimals. The infinitesimals that make up a specific region are translations of that region's right edge. 
The following observations can be made by inspecting Fig.\ref{??}: 
\begin{description}
 \item[Effect of $\alpha$] the grey-tinted solid curves depicted in each panel are not equal to one-another.
 \item[Effect of $t$] the dashed grey curves and the solid grey-tinted curves in the right-most panel are not equal to one-another.
\end{description}
We can therefore draw the following conclusion: the value of both $\alpha$ and $t$ alters the shape of the infinitesimals that make up the regions in Fig~\ref{??}. Interestingly, the effect of $\alpha$ on the shape of the infinitesimals that make up the regions depicted in Fig~\ref{??} is larger than the effect that $t$ has on their shape. 
The curves associated with the infinitesimals obtained by varying $t$, whilst keeping the value of $\alpha$ fixed are very similar in nature and there exists a high degree of correlation between them (if their 
size are ignored). The curves associated with the infinitesimals obtained by varying $\alpha$, whilst keeping the value of $t$ fixed are quite different from one another (the aforementioned curves are not highly correlated with 
one another).

@@

If we evaluate the integral in Eq for all $\alpha\in \mathsf{A}$ we obtain the curves in the left-most column of Table.... These curves are depicted in Fig.
The area of the regions depicted in Fig are also plotted in Fig using circular markers. As expected, the circular markers that correspond to the areas of the regions 
from a particular choice of $\alpha$ (i.e. from a particular panel of Fig) in Fig lie on the curve in Fig that is associated with the same choice of $alpha$. Moreover, note that we have adopted the 
same color scheme in Fig and Fig. Using the same color scheme in both Figures makes it clear which of the area values in Fig can be associated with which regions in Fig.

>>>>

If we set the value of $\alpha$ to $\sfrac{4}{5}$ and the value of $t$ to 10 in Eq.~\eqref{eq:ex1} we obtain:
\begin{equation}
\label{eq:ex1_specific}
A_{10}^{\sfrac{4}{5}}=\int_{a_{10}^{\frac{4}{5}}(y)}^{b_{10}^{\frac{4}{5}}(y)} f(\tau)~d\tau 
\end{equation}
Let $R_{10}^{\sfrac{4}{5}}$ denote the region which is bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{10}^{\sfrac{4}{5}}(y)$. The region $R_{10}^{\sfrac{4}{5}}$ is depicted and labelled in the right-most panel of Figure.~\ref{??}. 
Moreover, let $A_{10}^{\sfrac{4}{5}}$ denote the area of $R_{10}^{\sfrac{4}{5}}$. We are now in a position to assign a geometric interpretation to Eq.~\eqref{eq:ex1_specific} as it 
contains a Cavalieri integral. We can approximate the area of $A_{10}^{\sfrac{4}{5}}$ by summing together the area of $n$ equal width non-rectangular integration strips that inscribe $R_{10}^{\sfrac{4}{5}}$. 
Furthermore, the sides of these non-rectangular integration strips have to be translations of $b_{10}^{\sfrac{4}{5}}(y)$.
If we take the limit of the aforementioned sum as $n\rightarrow \infty$ we obtain $A_{10}^{\sfrac{4}{5}}$, i.e. the region $R_{10}^{\sfrac{4}{5}}$ is made up 
of an infinite number of infinitesimals; all of them being translations of $b_{10}^{\sfrac{4}{5}}(y)$. The special case in which we approximate $A_{10}^{\sfrac{4}{5}}$ using five equal width non-rectangular integration strips is depicted in the right-most panel of Figure~\ref{??}. 
The sides of the aforementioned five integration strips are depicted in Fig.~\ref{??} using dashed lines. Let $\mathsf{B}_{10}^{\sfrac{4}{5}}$ denote the set containing these dashed curves.

Varying both $\alpha$ and $t$ results in Eq.~\eqref{eq:ex1}. In contrast with Eq.~\eqref{eq:ex1_specific}, Eq.~\eqref{eq:ex1} can be associated with more than one region. 
Let $R_{t}^{\alpha}$ denote the region which is bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{t}^{\alpha}(y)$. Moreover, let $A_{t}^{\alpha}$ denote the area of $R_{t}^{\alpha}$ and let $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}=\{R_t^{\alpha}|t\in\mathsf{T},~\alpha\in\mathsf{A}\}$. 
The regions in the set $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}$ are depicted in Fig.~\textbf{??}. The regions that are depicted in each of the panels of Fig.~\ref{??} were generated by varying $t$, whilst keeping the value of $\alpha$ fixed. 
The title of each panel indicate which $\alpha$-value was used to generate the regions depicted in each panel. The only difference between the regions located in each 
panel is their right edges. The right edges of the regions in each panel are depicted using varying shades of gray. The lighter the shade with which an edge is depicted, 
the larger the $t$-value is, that was used to generate it.

As was the case for $R_{10}^{\sfrac{4}{5}}$, each of the regions depicted in Fig.~\ref{} are made up of an infinite number of infinitesimals. The infinitesimals that make up a specific region are translations of that region's right edge. 
The following observations can be made by inspecting Fig.\ref{??}: 
\begin{description}
 \item[Effect of $\alpha$] the grey-tinted solid curves depicted in the different panels of Fig.~\ref{} are not equal to one-another.
 \item[Effect of $t$] the grey-tinted solid curves depicted in each of the panels of Fig.~\ref{} are not translations of one-another. Moreover, the dashed grey curves and the solid grey-tinted curves in the right-most panel are not equal to one-another.
\end{description}
We can therefore draw the following conclusion: the value of both $\alpha$ and $t$ alters the shape of the infinitesimals that make up the regions in Fig~\ref{??}. Interestingly, the effect of $\alpha$ on the shape of the infinitesimals that make up the regions depicted in Fig~\ref{??} is larger than the effect that $t$ has on their shape. 
The curves associated with the infinitesimals obtained by varying $t$, whilst keeping the value of $\alpha$ fixed are very similar in nature and there exists a high degree of correlation between them (if their 
size are ignored). The curves associated with the infinitesimals obtained by varying $\alpha$, whilst keeping the value of $t$ fixed are quite different from one another (the aforementioned curves are not highly correlated with 
one another).

@@

If we evaluate the integral in Eq.~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ we obtain the curves in the left-most column of Table~\ref{??}. These curves are depicted in Fig~\ref{??}.
The area of the regions depicted in Fig.~\ref{??} are also plotted in Fig.~\ref{??} using circular markers. As expected, the circular markers in Fig.~\ref{??} that correspond to the areas of the regions in Fig.~\ref{??}  
associated with a particular choice of $\alpha$ (i.e. regions depicted in a particular panel of Fig.~\ref{??}) fall on the curve in Fig.~\ref{??}; associated with the same choice of $\alpha$. Moreover, note that we have adopted the 
same coloring scheme in Fig.~\ref{??} and Fig.~\ref{??}. Using the same coloring scheme in both figures makes it clear which of the area values in Fig.~\ref{??} can be associated with which regions in Fig.~\ref{??}.
To summarize, Fig.~\ref{??}, therefore, depicts a non-static non-rectangular sum-based geometric interpretation of Eq.~\eqref{}. Moreover, Fig.~\ref{??} corroborates this 
geometric interpretation.

Let us know consider a different fractional integral:
\begin{equation}
\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \frac{1}{\Gamma(\alpha)}\int_0^t \sqrt{\tau}(t-\tau)^{\alpha-1}~d\tau. 
\end{equation}
If we evaluate the integral in Eq.~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ we obtain the curves in the right-most column of Table~\ref{??}. These curves are depicted in Fig~\ref{??}.
The non-static non-rectangular sum-based geometric interpretation associated with Eq.~\eqref{eq:ex1} is depicted in Fig. The validity of this interpretation is corroborated by Fig.

To conclude this section, a fractional integral of order $\alpha$ and extent $t$ can be interpreted as the area obtained by summing together the area associated with an infinite number of infinitesimals whose 
shape is determined by $\alpha$ and $t$. The geometric interpretation of a fractional integral is, therefore, non-static as it depends on the value of both $\alpha$ and $t$.

%the fractional integral in Eq.~\ref{??} can be interpreted as the area which is obtained by summing together the area associated with an infinite number of non-rectangular infinitesimals whose shape 
%is determined by the integration limits of the Cavalieri integral. Note that neither $g_t^{\alpha}(\tau)$ nor $a_t^{\alpha}(y)$ are static functions, 
%they depend on the value of $\alpha$ and $t$. This implies that a fractional integral of order $\alpha$ and extent $t$ can be interpeted as the area obtained by summing together the area associated with an infinite number of infinitesimals whose 
%shape is determined by $\alpha$ and $t$, i.e. the geometric interpretation of Eq.~\eqref{eq:ex1_raw} is non-static as it depends on the value of $\alpha$ and $t$.
